%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeHeading
        {Admire Creations}{Ernakulam, Kerala, India}
        {Technical Lead, Co-founder}{Dec 2022 -- Present}
        \resumeItemListStart
            \resumeItem{As a co-founder, I’m in charge of understanding the market as it stands, assigning and managing projects, and exploring various growth opportunities for the company.}
            \resumeItem{As a Developer, I work with React.js, WordPress, Figma, various deployment platforms, and headless CMS solutions to meet our client requirements.}
        \resumeItemListEnd

        \vspace{4pt}
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            {\textbf{Indic Law} $|$ \emph{Startup}} & {Ernakulam, Kerala, India} \\
        \end{tabular*}\vspace{-6pt}

        \resumeSubHeading
        {Front-end Developer}{Sept 2021 -- Nov 2022}
        \resumeItemListStart
            \resumeItem{Solely designed and developed a custom CMS for managing the content of the app and website using React.js following the Ant Design System.}
            \resumeItem{Designed and developed a single static page for marketing purposes using HTML, CSS, and simple PHP for form handling and ERPNext integration.}
        \resumeItemListEnd
        
        \resumeSubHeading
        {Project Manager}{Sept 2021 -- Nov 2022}
        \resumeItemListStart
            \resumeItem{Managed a collaborative joint tech team in developing an edu tech platform on both mobile and web.}
            \resumeItem{Administration and management of the company AWS, GitHub organisation workspace.}
            \resumeItem{Assist the internal team with concerns regarding ERPNext.}
        \resumeItemListEnd

        \resumeSubHeading
        {DevOps Engineer}{Sept 2021 -- Nov 2022}
        \resumeItemListStart
            \resumeItem{Pushed myself to take charge of understanding AWS as part of project management to implement CI CD pipelines for the back-end using Docker, Jenkins scripts, EC2, AWS ECR, AWS IM, AWS Route 53, and ACM. We also used AWS Amplify to host the website.}
            \resumeItem{Explored the vast ocean of AWS EKS by implementing gitops with argocd, cert-manager and Nginx Ingress Controllers. I also tried AWS CodeDeploy and AWS ECS.}
        \resumeItemListEnd

        \resumeSubHeading
        {Back-end Developer}{Sep 2021 -- Nov 2022}
        \resumeItemListStart
            \resumeItem{Worked with an Express.js + MongoDB codebase on AWS.}
            \resumeItem{Assisted in refactoring the old codebase by versioning and modularizing with better flexibility.}
            \resumeItem{Wrote RESTful APIs for the CMS of the app and website. Implemented role-based and module permission-based editing after being inspired by ERPNext.}
        \resumeItemListEnd

        \resumeSubHeading
        {User Interface Designer}{Oct 2020 -- Aug 2021}
        \resumeItemListStart
            \resumeItem{Was in charge of solely prototyping and designing an MVP mobile app in the “edu tech” space using Figma.}
            \resumeItem{Worked with a fresh team of developers from college, content writers, and people who dared take action on their collected vision.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
